---
title: "5291 final"
author: "Yiyang Fu yf2473"
date: "5/5/2019"
output:
  html_document: default
  word_document: default
---


### 1. Summary



### 2. Introduction
EDA
```{r}
library(data.table)
library(corrplot)
data <- read.table("../Project/CRIMEDATA.txt", sep="", header=FALSE)
UNI <- 2473
set.seed(UNI)
index <-sample(c(1:440))
mydata<-data[index[1:250],]
mydata <- as.data.table(mydata)


data.name <- c("Identification_Number","County_Name","State","Land_area","Total_population","P18_34","P65","active_physicians","hospital_beds","serious_crimes","P_highschool_graduate","P_bechelor's","P_lowpoverty","P_unemployment","capita_income","total_personal_income","Geographic_region")
colnames(mydata)<- data.name

#mydata.scale <- mydata[, lapply(.SD, scale, center = FALSE), .SDcols = data.name[-c(1,2,3,17)]]

#mydata$Geographic_region <- as.factor(mydata$Geographic_region)
mydata$Land_area <- mydata$Total_population/mydata$Land_area
mydata$active_physicians <- (mydata$active_physicians/mydata$Total_population)*100
mydata$hospital_beds <- (mydata$hospital_beds/mydata$Total_population)*100
mydata$crimerate <- (mydata$serious_crimes/mydata$Total_population)*100
mydata[, Total_population := NULL]
mydata[, total_personal_income := NULL]
mydata[, serious_crimes := NULL]

par(mfrow=c(3,4),mar=rep(2,4),oma=c(0,0,2,0))
#boxplot(mydata$crimerate, mydata$P18_34, mydata$P65, mydata$active_physicians, mydata$hospital_beds, mydata$P_highschool_graduate, mydata$`P_bechelor's`, mydata$P_lowpoverty, mydata$P_unemployment, mydata$Geographic_region)
boxplot(mydata$crimerate)
boxplot(mydata$P18_34)
boxplot(mydata$P65)
boxplot(mydata$active_physicians)
boxplot(mydata$hospital_beds)
boxplot(mydata$P_highschool_graduate)
boxplot(mydata$`P_bechelor's`)
boxplot(mydata$P_lowpoverty)
boxplot(mydata$P_unemployment)
boxplot(mydata$capita_income)
boxplot(mydata$Geographic_region)

```

Check mean and standard deviation of data:
```{r}
mydata[, lapply(.SD, mean, na.rm=TRUE), .SDcols = data.name[-c(1,2,3,5,10,16)]]
mydata[, lapply(.SD, sd, na.rm=TRUE), .SDcols = data.name[-c(1,2,3,5,10,16)]]
```

Clean data: 

We added crime rate variable which is calculated by serious crimes number divided by total population. And we also added population rate calculated by total population divided by land area.



### 3. Results
Build model: Linear Regression
```{r}
model <- lm(crimerate~., data = mydata[, -c(1,2,3)])
summary(model)
```

Confidence Interval
```{r}
confint(model)
```

Residual Analysis
```{r}
par(mfrow = c(2,2))
plot(model)

#remove the 162 pot
mydata <- mydata[-162, ]
model <- lm(crimerate~., data = mydata[, -c(1,2,3)])
summary(model)
```

```{r}
par(mfrow = c(2,2))
plot(model)
```




Check correlation
```{r}
x <- cor(mydata[, -c(1,2,3,14)],use = "pairwise.complete.obs")
cor.list <- as.data.frame(as.table(x))
cor.list <- cor.list[0.5 < cor.list$Freq,]
cor.list <- cor.list[cor.list$Freq < 1,]

corrplot(x, type="upper", order="hclust",tl.col = "black", tl.cex = 0.7, cl.cex = 0.7, addCoef.col="grey", number.cex = 0.45)

```
From the correlation plot, we can see that several variables are highly correlated. 


Improve model: simply select significant variables from original linear regression model
```{r}
model.lm <- lm(crimerate~Land_area+hospital_beds+P_highschool_graduate+P_lowpoverty+Geographic_region, data = mydata)
summary(model.lm)
```


Stepwise: Selecting variables by AIC stepwise function
Examine our variable selection result 
```{r, include=FALSE}
library(MASS)
lm.null <- lm(crimerate ~., data = mydata[, -c(1,2,3,10)])
lm.full <- lm(crimerate ~ (.)^2, data = mydata[, -c(1,2,3,10)])
stepwise.selection <- stepAIC(lm.null, direction = "both", scope = list(upper = lm.full, lower = lm.null))

```

```{r}
summary(stepwise.selection)
```

```{r}
par(mfrow = c(2,2))
plot(stepwise.selection)
```






